Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-14 ms.qmd
Fixed figures

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: true
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: '**Fig**'
  fig-labels: arabic
  title-delim: "**-**"
  fig-prefix: "Figure"
  tbl-labels: "**Table**"
---

@@

    # Add slopes and 95% CI to each panel
    # CV
    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))

    # ACF
    posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")

dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
                      condition = c("f", "m", "t"),
                      x = rep(1.2, 3),
                      y = rep(-1.2, 3))

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col)) + geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7)

dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
                      condition = c("f", "m", "t"),
                      x = rep(1.2, 3),
                      y = rep(-1.2, 3))

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col)) geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7)

p8.1.2 <- p8.1 / p8.2
p8.1.2
ggsave(p8.1.2, filename = "./output/figures/fig8.png")
```

>>>>

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: '**Fig**'
  fig-labels: arabic
  title-delim: "**-**"
  fig-prefix: "Figure"
  tbl-labels: "**Table**"
---

@@

size_axis = 18
# CV
dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
                      title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(1.2, 3),
                      y = rep(-1.2, 3))

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7) + 
geom_text(data = dat_text, aes(x = x, y = y-0.2, label = label2), size = 7) +
geom_text(data = dat_text, aes(x = x, y = y-0.4, label = p), size = 7) +
geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 7) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

  # ACF
dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
                      condition = c("f", "m", "t"),
                      x = rep(-2.8, 3),
                      y = rep(-1.2, 3))

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.2, label = label2), size = 7) +
geom_text(data = dat_text2, aes(x = x, y = y-0.4, label = p), size = 7) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")")

ggsave(p8.1.2, width = 13, height = 12.5, filename = "./output/figures/fig8.png")

  p8.1.2 <- image_read("./output/figures/fig8.png")
p8.1.2
```
